\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-28 methodology.tex
added some extra text and code

\PDComment{Do we want to actually mention (and compare with) P in this paper?}
%The \psharp language belongs to the same family of languages as P~\cite{desai2013p}.

\subsection{Methodology}
\label{sec:method:new}

@@

Draft.

@@

\begin{figure}[t]
\begin{lstlisting}
// Public interface of the real network engine
class NetworkEngine {
  public virtual void SendMessage();
  public virtual void EnqueueMessage();
}

@@

\subsection{Extensibility of the \psharp framework}
\label{sec:method:extend}

@@

>>>>

%The \psharp language belongs to the same family of languages as P~\cite{desai2013p}.

@@

@@

\begin{figure}[t]
\begin{lstlisting}
// Public interface of the real network engine
class NetworkEngine {
  public virtual void SendMessage(Socket s, Message msg);
  public virtual void EnqueueMessage(Message msg);
}

@@

\subsection{Abstracting timers}
\label{sec:method:timers}

Distributed systems are often using timers to determine when an event should be fired. For example, in the Azure Storage vNext system, each Extent Node is associated with a timer that fires of a synchronization message every 5 minutes and a heartbeat every 5 seconds. However, when testing to find bugs, these timers should be abstracted away and be triggered nondeterministically.

Figure~\ref{fig:timer} shows how we modeled timers in Azure Storage vNext. Each ExtentNode in the harness is associated with a unique \texttt{Timer} machine. Each \texttt{Timer}, when transitions to the \texttt{Active} state, loops infinitely and nondeterministically sends a \texttt{TimerTickEvent} to \texttt{this.Target}.

\begin{figure}[t]
\begin{lstlisting}
internal class Timer : Machine
{
  MachineId Target;
  string Info;

  [Start]
  [OnEntry(nameof(InitOnEntryAction))]
  [OnEventGotoState(typeof(Unit), typeof(Active))]
  class Init : MachineState { }

  void InitOnEntryAction()
  {
    this.Target = (MachineId)(this.Payload as object[])[0];
    this.Info = (string)(this.Payload as object[])[1];
    this.Raise(new Unit());
  }

  [OnEntry(nameof(ProcessTickEvent))]
  [OnEventGotoState(typeof(Unit), typeof(Active))]
  class Active : MachineState { }

  void ProcessTickEvent()
  {
    if (this.Nondet())
    {
      this.Send(this.Target, new TimerTickEvent());
    }

    this.Raise(new Unit());
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Timers in Azure Storage vNext are modeled as a nondeterministic \psharp machines.}
\label{fig:timer}
%\vspace{-2mm}
\end{figure}

\subsection{Abstracting node expiration}
\label{sec:method:timers}

Node expiration

\begin{figure}[t]
\begin{lstlisting}
public virtual bool IsNodeExpired(string node_id, DateTime expiration)
{
  return DateTime.Compare(expiration, DateTime.Now) <= 0;
}

public override bool IsNodeExpired(string node_id, DateTime expiration)
{
  return deletedNodes.Contains(node_id);
}
\end{lstlisting}
\vspace{-2mm}
\caption{draft}
\label{fig:expiration}
%\vspace{-2mm}
\end{figure}

\subsection{Handling intra-machine concurrency}
\label{sec:method:async}

@@

\subsection{Other}
\label{sec:method:other}
